### 2016-05-09 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More home edits

#First calculate Delta RTL 
temp <- subset(dd,!duplicated(paste0(BirdID,Agemonths)))
counts <- with(temp,tapply(RTL,BirdID,length))
c3 <- names(counts[counts >= 2])
dd3 <- subset(temp,BirdID %in% c3)
DeltaRTL <- NA

for(i in 1:nrow(dd3))
{
  cd <- subset(dd3,BirdID == dd3$BirdID[i])
  cd <- cd[order(cd$Agemonths),]

  birdpos <- which(cd$BloodID == dd3$BloodID[i])

  if(birdpos == 1)
  {
    dd3$DeltaRTL[i] <- 0
  } else
  {
      prevbird <- cd[birdpos-1,'RTL']
  dd3$DeltaRTL[i] <- dd3$RTL[i]-prevbird
  dd3$MidAge[i] <- mean(c(dd3$Agemonths[i],cd[birdpos-1,'Agemonths']))
  dd3$MinAge[i] <- cd[birdpos-1,'Agemonths']
  dd3$TimeDiff[i] <- dd3$Agemonths[i] - cd[birdpos-1,'Agemonths']
  }

}

temp <- subset(dd0,!duplicated(paste0(BloodID,RTL)))
temp <- subset(temp,RTL<2)
temp <- subset(temp,RTL > 0.04)

counts <- with(temp,tapply(RTL,BloodID,length))
c3 <- names(counts[counts %in% c(2:5)])

dd3_2 <- subset(temp,BloodID %in% c3)
dd3_2 <- dd3_2[order(dd3_2$BloodID),]
counts <- with(dd3_2,tapply(RTL,BloodID,length))

dd3_2$birdpos <- unlist(sapply(counts,function(x) c(1:x)))

dd3_2$DeltaRTL <- NA

for(i in 1:nrow(dd3_2))
{
  cd <- subset(dd3_2,BloodID == dd3_2$BloodID[i])

  if(dd3_2$birdpos[i] == 1)
  {
    dd3_2$DeltaRTL[i] <- 0
  } else
  {
      prevbird <- subset(cd,birdpos == dd3_2$birdpos[i]-1)$RTL
  dd3_2$DeltaRTL[i] <- dd3_2$RTL[i]-prevbird
  }

}

dd3 <- subset(dd3,DeltaRTL !=0)
dd3_2 <- subset(dd3_2,DeltaRTL!=0)
dd3_2 <- dd3_2[1:nrow(dd3),]

temp <- data.frame(DeltaRTL = c(dd3$DeltaRTL,dd3_2$DeltaRTL),Group = rep(c('Among samples','Within samples'),c(nrow(dd3),nrow(dd3_2))))

Fig4C <- ggplot(temp,aes(col=Group,fill = Group,x = DeltaRTL, y = ..scaled..))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.22,0.78),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)+
  annotate('text',x = -2,y = 1,label = 'C')

@@

>>>>

Fig4C <- ggplot(ddL,aes(col=Group,fill = Group,x = DeltaRTL, y = ..scaled..))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.22,0.78),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)+
  annotate('text',x = -2,y = 1,label = 'C')

@@

ddL <- ddL[complete.cases(ddL),]
